Incorporating periodic variability in hidden Markov models for animal movement

### 2016-03-14 paper3.Rnw
update encircle

\doublespacing
<<pkgs,message=FALSE,warning=FALSE,echo=FALSE>>=
library("ggplot2"); theme_set(theme_bw())
scale_colour_discrete <- function(...,palette="Set1")
    scale_colour_brewer(...,palette=palette)
scale_fill_discrete <- function(...,palette="Set1")
    scale_fill_brewer(...,palette=palette)
zmargin <- theme(panel.margin=grid::unit(0,"lines"))
library("knitr")
opts_chunk$set(fig.width=6,fig.height=4)
library("depmixS4")
library("plyr")
library("dplyr")
library("reshape2")
library("gridExtra")
@

@@

<<state_plots, warning=FALSE, message=FALSE, echo=FALSE, fig.cap="Step-length parameters (\\textbf{todo: change scales from log() to log-scale}">>=
source("bhull.R")
g0 <- ggplot(all_cat_pars,aes(log_mean,log_sd,color=Model))+
    geom_point()+geom_line() + facet_wrap(~catID,labeller=label_both)+zmargin
g0 +
    geom_encircle(data=subset(all_cat_pars,
                              (catID=="15" & log_mean<1.5) |
                              (catID!="15" & log_mean<1.8)),
                  colour="black",linetype=2,expand=0.05)
@

>>>>

\doublespacing
<<pkgs,message=FALSE,warning=FALSE,echo=FALSE>>=
library("ggplot2"); theme_set(theme_bw())
scale_colour_discrete <- function(...,palette="Set1")
    scale_colour_brewer(...,palette=palette)
scale_fill_discrete <- function(...,palette="Set1")
    scale_fill_brewer(...,palette=palette)
zmargin <- theme(panel.margin=grid::unit(0,"lines"))
library("knitr")
opts_chunk$set(fig.width=6,fig.height=4)
library("depmixS4")
library("plyr")
library("dplyr")
library("reshape2")
library("gridExtra")
if (!require("ggalt")) {
    cat("installing ggalt from BB repo ...\n")
    library("devtools")
    install_github("bbolker/ggalt")
    library("ggalt")
}
@

@@

<<state_plots, warning=FALSE, message=FALSE, echo=FALSE, fig.cap="Step-length parameters (\\textbf{todo: change scales from log() to log-scale}">>=
g0 <- ggplot(all_cat_pars,aes(log_mean,log_sd,color=Model))+
    geom_point()+geom_line() + facet_wrap(~catID,labeller=label_both)+zmargin
(g0c <- g0 +
    geom_encircle(data=subset(all_cat_pars,
                              (catID=="15" & log_mean<1.5) |
                              (catID!="15" & log_mean<1.8)),
                  colour="black",linetype=2,expand=0.05))
@
